### 2018-05-17 manuscript.rmd
update Figure references

ML analyses were conducted on the unpartitioned supermatrix using the WAG+$\Gamma$ model of amino acid substitution, and bootstrap values were estimated using `r length(bootstrap_trees)` replicates. BI was conducted using two different CAT models, CAT-Poisson and CAT-GTR [@doi:10.1093/molbev/msh112]. Two independent MCMC chains were run under the CAT-GTR model, and eight independent MCMC chains were run under the CAT-Poisson model. The BI analyses did not converge (CAT-Poisson: maxdiff=1, meandiff=0.0185032; CAT-GTR: maxdiff=1, meandiff=0.045415). Only the results from the CAT-Poisson model are presented here. Two chains (chain1 and chain3) were stuck in local maxima after 1405 and 4695 iterations and were excluded from the analyses. Visual inspection of the traces indicated that a burn in of `r burn_in` trees was sufficient for all CAT-Poisson runs. This left `r length( phylobayes_trees )` trees in the posterior.

To test the robustness of the results to model selection, we also used IQTree to implement other ML analyses using different models of substitution [@doi:10.1093/molbev/msu300; @doi:10.1093/molbev/msx281].  We also evaluated effects of method (ML vs. BI), model, and program by running a fixed-state WAG+$\Gamma$ model in Phylobayes and an ML approximation of CAT models in IQTree.

>>>>

ML analyses were conducted on the unpartitioned supermatrix using the WAG+$\Gamma$ model of amino acid substitution, and bootstrap values were estimated using `r length(bootstrap_trees)` replicates. BI was conducted using two different CAT models, CAT-Poisson and CAT-GTR [@doi:10.1093/molbev/msh112]. Two independent MCMC chains were run under the CAT-GTR model, and eight independent MCMC chains were run under the CAT-Poisson model. The BI analyses did not converge (CAT-Poisson: maxdiff=1, meandiff=0.0185032; CAT-GTR: maxdiff=1, meandiff=0.045415). Only the results from the CAT-Poisson model are presented here (Fig. S11). Two chains (chain1 and chain3) were stuck in local maxima after 1405 and 4695 iterations and were excluded from the analyses. Visual inspection of the traces indicated that a burn in of `r burn_in` trees was sufficient for all CAT-Poisson runs. This left `r length( phylobayes_trees )` trees in the posterior.

To test the robustness of the results to model selection, we also used IQTree to implement other ML analyses using different models of substitution [@doi:10.1093/molbev/msu300; @doi:10.1093/molbev/msx281].  We also evaluated effects of method (ML vs. BI), model, and program by running a fixed-state WAG+$\Gamma$ model in Phylobayes (Fig. S12) and an ML approximation of CAT models in IQTree (Fig. S10).
